\documentclass[letterpaper,12pt]{extarticle}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{multicol}

\titleformat{\section}
{\Large\bfseries\uppercase}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\large}
{}
{0em}
{$\bullet$ }

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{- }[ :]

\titlespacing{\subsubsection}
{0em}{.25em}{1em}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\newcommand{\organization}[4] {
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
		\textbf{\large#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-10pt}
}

\title{R\'esum\'e}
\author{Vikas Kushwaha}

\begin{document}

\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
	\href{https://vikas.rocks}{\underline{vikas.rocks}} &
	\href{https://vikas.rocks}{\Large\bfseries \theauthor} &
	\href{tel:+917498130470}{+91 7498 1305 70} \\
	Mumbai, Maharashtra &
	(Student) \thetitle &
	csstudent41@gmail.com
\end{tabular*}

\section{Technical Skills}

\begin{minipage}[t]{0.5\textwidth}
	\subsection{Languages} Languages listed in decreasing order of competence.
	\subsubsection{Programming} C/C++, Go, JavaScript
	\subsubsection{Scripting} Shell, Python, Awk, R
	\subsubsection{Markup} HTML, CSS, {\LaTeX}
	\subsubsection{Database}
	MySQL, Oracle, MongoDB
\end{minipage}
\hfill
\vrule
\hfill
\begin{minipage}[t]{0.45\textwidth}
	\subsection{Work Flow}
	\subsubsection{OS} Arch Linux
	\subsubsection{Window Manager} i3
	\subsubsection{Text Editor} vim
	\subsubsection{Remote Management} ssh, tmux, git, rsync, syncthing
\end{minipage}


\section{Education}

\organization
{\href{https://avc.ac.in}{Annasaheb Vartak College}} {Vasai West, Mumbai}
{B.Sc. Computer Science (ongoing)} {2022 - 2024}


\section{Experience}

\subsubsection{Web} I have some expreience in building static websites. I can build a python web server (using Flask) or a Go server (using net/http). I briefly touched AngularJS, Express and NodeJS and and can pick them up anytime when needed.

\subsubsection{Application} Have little experience in developing Python Tkinter application. Worked with Java Swing and Flutter during uni.

\subsubsection{Linux} I use a linux computer on a daily basis. It's heavily customized by me. I use debian server on my RasberryPi.

\subsubsection{Scripting} I have written a lot of shell scripts. I have done more scripting than programming.


\section{Notable Projects}
Most things here can be found on my GitHub page. (\url{https://github.com/csstudent41})

\subsubsection{My Personal Website} Build by me (ofcourse), using Hugo. Link on top.

\subsubsection{BITS24 Website}
There was a Techfest event hosted in our college called BITS which was organised by us. Me and my friends build the website for BITS (January 2024). The website is hosted on onrender \underline{\url{https://bits24.onrender.com}} and it's source files are on our commitee's github account \underline{\url{https://github.com/vtc-tech/bits24}}.

\subsubsection{Scraping Exam Results} I scraped my college exam result's PDF(s), extracted student's data and turned them into web pages (\underline{\url{https://vikas.rocks/results}}). Used awk and a bunch of shell scripts for this.

\end{document}
